% ========================================
% COVER LETTER DATA - Edit this file with your information
% ========================================

% YOUR INFORMATION
\def\CLFirstName{John}
\def\CLLastName{Doe}
\def\CLPhone{(555) 123-4567}
\def\CLEmail{john.doe@email.com}
\def\CLLinkedIn{linkedin.com/in/johndoe}
\def\CLAddress{123 Main Street, San Francisco, CA 94102}

% DATE
\def\CLDate{\today}  % Or specify a date like: January 22, 2025

% RECIPIENT INFORMATION
\def\CLHiringManager{Jane Smith}
\def\CLCompany{Tech Innovations Inc.}
\def\CLCompanyAddress{456 Innovation Drive}
\def\CLCompanyCity{San Francisco, CA 94103}

% SUBJECT LINE (optional)
\def\CLSubject{Application for Senior Software Engineer Position}

% LETTER CONTENT
\def\CLOpeningParagraph{%
I am writing to express my strong interest in the Senior Software Engineer position at Tech Innovations Inc. With over 5 years of experience in full-stack development and a proven track record of delivering scalable solutions, I am excited about the opportunity to contribute to your team's success.
}

\def\CLBodyParagraphOne{%
In my current role at Tech Company Inc., I have led the development of microservices architecture serving over 1 million daily users, improving system reliability by 40\%. I architected and implemented a CI/CD pipeline that reduced deployment time from 2 hours to just 15 minutes, significantly accelerating our development cycle. My expertise in React, Node.js, and cloud technologies aligns perfectly with the requirements outlined in your job posting.
}

\def\CLBodyParagraphTwo{%
What particularly excites me about Tech Innovations Inc. is your commitment to pushing the boundaries of technology while maintaining a strong focus on user experience. Your recent launch of the AI-powered analytics platform demonstrates the kind of innovative thinking that I am passionate about contributing to. I am confident that my experience in building scalable systems and my collaborative approach to problem-solving would make me a valuable addition to your engineering team.
}

\def\CLBodyParagraphThree{%
Beyond my technical skills, I bring strong leadership abilities, having mentored a team of 5 junior developers and conducted regular code reviews and training sessions. I am committed to writing clean, maintainable code and fostering a culture of continuous improvement within development teams.
}

\def\CLBodyParagraphFour{}

\def\CLBodyParagraphFive{}

\def\CLClosingParagraph{%
I would welcome the opportunity to discuss how my skills and experience align with your team's needs. Thank you for considering my application. I look forward to the possibility of contributing to Tech Innovations Inc.'s continued success.
}

% CLOSING
\def\CLClosing{Sincerely}  % Or: Best regards, Respectfully, etc.

% SIGNATURE (optional - path to signature image)
\def\CLSignature{}  % Leave empty or specify path like: signatures/signature.png
